---
title: "Knapsack problem"
author: "Roshni , Mariano and Pedram"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Google API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette summarizes three functions of Knapsack package and gives examples on how to use them.
The 3 functions are,

1. Brute force algorithm
2. Dynamic algorithm
3. Greedy algorithm

### Dynamic algorithm

The function knapsack_dynamic takes a data.frame x with two variables v and w and returns the maximum knapsack value and which elements (rows in the data.frame).

```{r}
knapsack_dynamic <- function(x, W){
  stopifnot(is.data.frame(x) == TRUE)
  stopifnot(is.numeric(W) == TRUE)
  n <- nrow(x)
  w <- x[[1]]  #weights
  v <- x[[2]]  #values
  cap <- W     #capacity of knapsack
  elem <- c()
  m <- matrix(0,nrow = n+1,ncol = cap+1)
 
  #to return the max value 
  for (i in 2:n){
    for (j in 1:cap){
      if (w[i] > j) 
        m[i,j] <- m[i-1, j]
      else 
        m[i, j] <- max(m[i-1, j], m[i-1, j-w[i]] + v[i])
    }
  }
  
  val <- m[i, j]
  value <- round(val)
  
  #to print the elements
  while(cap>0 && n-1>0){
    if(m[n,cap]!=m[n-1,cap]){
      elem<-c(elem,n)
      cap<-cap-w[n]
      elements <- sort(elem)
    }
    n<-n-1
  }
  return(list("value"=value,"elements"=elements))
  
}
```

### Examples

#### For brute force method

```{r}
set.seed(42)
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )
#brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```


#### For dynamic approach

```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 2000)
```

#### For greedy approach
```{r}
#greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
```

### Run time calculation

```{r}
start.time <- Sys.time()
knapsack_dynamic(x = knapsack_objects[1:8,], W = 2000)
end.time <- Sys.time()
end.time - start.time
```

### References

1. "Description of Knapsack problem"
([via](https://en.wikipedia.org/wiki/Knapsack_problem))

2. "Pseudocode to implement dynamic algorithm"
([via](https://en.wikipedia.org/wiki/Knapsack_problem#0.2F1_knapsack_problem))

3. "To implement greedy approach"
([via](https://en.wikipedia.org/wiki/Knapsack_problem#Greedy_approximation_algorithm))

4. "To measure the run time of code chunk"
([via](https://www.r-bloggers.com/5-ways-to-measure-running-time-of-r-code/))